---
title: "Finding Meaningful Demographic, Clinical, and Surgical Factors among Patients Treated for Torn Rotator Cuff"
author: "Jay Kim"
date: "5/18/2021"
output: html_document
---

#Finding Meaningful Demographic, Clinical, and Surgical Factors among Patients Treated for Torn Rotator Cuff

## Descriptive Statistics



```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
set.seed(123)
library(qwraps2)
options(qwraps2_markup="markdown")
library(gtsummary); library(gt); library(survival)
library(dplyr); library(stringr); library(purrr); library(forcats); library(tidyr)
getwd()
```

```{r}
library(readr)
PASTA_data_clean2 <- read_csv("G:/My Drive/#1_Jay's Space/Andrews_Insititute/PASTA/PASTA_data_clean2.csv", 
    col_types = cols(`Patient #` = col_factor(levels = c())))
library(janitor)
PASTA_Data1 <- clean_names(PASTA_data_clean2) 

```

### Univariate regression table

```{r}
library(tidyverse)
library(ggpubr)
library(rstatix)
library(datarium)

#SANE 
PASTA_Data1 %>% 
  group_by(pass_n_no_y_yes) %>% 
  get_summary_stats(sane_score_0_100, type="five_number")

#ASES 
PASTA_Data1 %>% 
  group_by(pass_n_no_y_yes_3) %>% 
  get_summary_stats(ases_index_0_100, type="five_number")


library(Hmisc)
 des1 <- describe(PASTA_Data1)
 des1
 des2 <- tbl_summary(PASTA_Data1[,-1],
                     by=pass_total_ases_sane_n_no_y_yes) %>% 
   add_n() %>% 
   add_p() %>% 
   modify_header(label="**Overall Pass**") %>% 
   bold_labels()
   #add.significance.stars()
 
 des2
 
```

```{r}
table(PASTA_Data1$workers_compe_ation_claim, PASTA_Data1$laborer_yes_no)
table(PASTA_Data1$rheumatoid_arthritis_yes_no, PASTA_Data1$gout_yes_no)
table(PASTA_Data1$rheumatoid_arthritis_yes_no, PASTA_Data1$shoulder_arthritis_grade_0_4)

```




### boxplot by ASES and SAES score

```{r eval=FALSE, include=FALSE}
library(dplyr)
PASTA_Data2 <-  PASTA_Data1 %>% 
  mutate(shoulder_arthritis = as.factor(shoulder_arthritis_grade_0_4)) %>% 
  mutate(pass_total  = as.factor(pass_total_ases_sane_n_no_y_yes)) %>% 
  mutate(saneandases = sane_score_0_100+ases_index_0_100) %>% 
  select(2:28,40,ases_func_0_30,vas_0_10,pass_n_no_y_yes,pass_n_no_y_yes_3,pass_total,sane_score_0_100,ases_index_0_100,42 )

```

```{r echo=FALSE}
#following
library(dplyr)
library(janitor)
library(gtsummary)
#sane_five <- PASTA_Data2 %>% 
#  group_by(follow_up_years,pass_total) %>% 
#  get_summary_stats(sane_score_0_100, type="five_number")

#ases_five <- PASTA_Data2 %>% 
#  group_by(follow_up_years,pass_total) %>% 
#  get_summary_stats(ases_index_0_100, type="five_number")

library(plotly)
 fig1 <-  plot_ly() %>% 
  add_trace(data = PASTA_Data2,
            y = ~sane_score_0_100,
            color = ~pass_total,
            colors = "Dark2",
            type = "box") %>% 
  layout(title = "SANE Score by Overall Pass",
         xaxis = list(title = "Pass"))
 
fig2 <-   plot_ly() %>% 
  add_trace(data = PASTA_Data2,
            y = ~ases_index_0_100,
            color = ~pass_total,
            colors = "Dark2",
            type = "box") %>% 
  layout(title = "ASES Score by Overall Pass",
         xaxis = list(title = "Pass"))

```
```{r}
fig1
fig2
 


```

### scatter plot ASES va. SANE by overall PASS

```{r echo=FALSE}
library(highcharter)
PASTA_Data2 %>% 
  hchart(., type="scatter", hcaes( x= ases_index_0_100, y= sane_score_0_100, group = pass_total))
```




```{r eval=FALSE, include=FALSE}

library(rcompanion)
# SANE
CI_y <- as.data.frame.matrix(groupwiseMean(sane_score_0_100 ~ 1, data= PASTA_Data2, conf = 0.95))
CI_y$vari_name <- "SANE_score"
CI_y
#one way
CI_x1 <- as.data.frame.matrix(groupwiseMean(sane_score_0_100 ~ anxiety_depression_yes_no, data= PASTA_Data2, conf = 0.95))
CI_x1
##two way
CI_x2 <- as.data.frame.matrix(groupwiseMean(sane_score_0_100 ~ anxiety_depression_yes_no + shoulder_arthritis_grade_0_4 , data= PASTA_Data2, conf = 0.95))
CI_x2

# ASES
CI_y1 <- as.data.frame.matrix(groupwiseMean(ases_index_0_100 ~ 1, data= PASTA_Data2, conf = 0.95))
CI_y1$vari_name <- "ASES_score"
CI_y1
#one way
CI_x12 <- as.data.frame.matrix(groupwiseMean(ases_index_0_100 ~ anxiety_depression_yes_no, data= PASTA_Data2, conf = 0.95))
CI_x12
##two way
CI_x22 <- as.data.frame.matrix(groupwiseMean(ases_index_0_100 ~ anxiety_depression_yes_no + shoulder_arthritis_grade_0_4 , data= PASTA_Data2, conf = 0.95))
CI_x22


```

### for skewed data (bootstrapped CI may be more reliable)

```{r}
groupwiseMean(ases_index_0_100 ~ -1,
              data   = PASTA_Data2,
              conf   = 0.95,
              digits = 3,
              R      = 10000,
              boot        = TRUE,
              traditional = FALSE,
              normal      = FALSE,
              basic       = FALSE,
              percentile  = FALSE,
              bca         = TRUE)


groupwiseMean(sane_score_0_100 ~ -1,
              data   = PASTA_Data2,
              conf   = 0.95,
              digits = 3,
              R      = 10000,
              boot        = TRUE,
              traditional = FALSE,
              normal      = FALSE,
              basic       = FALSE,
              percentile  = FALSE,
              bca         = TRUE)

```
### using boot function

```{r}
library(boot)
myboot <- boot(PASTA_Data2$saneandases,
               function(x,i) mean(x[i]),
               R=10000)

mean(myboot$t[,1]) # mean based on bootstrap

boot.ci(myboot, cof=0.95,
        type=c("norm","basic","perc","bca"))

#hist
myboot
hist(myboot$t[,1], col="darkblue")

```

### Traditional way mean, sd, and CI using long data

```{r}
library(Rmisc)
PAST_num <-  PASTA_Data1 %>% 
  dplyr::select(-shoulder_arthritis_grade_0_4) %>% 
  select_if(is.numeric) %>% 
  as.list()

PAST_num_DF <- PAST_num  %>%  as.data.frame()
long_PAST <- gather(PAST_num_DF, factor_key = T)
 long_df <- long_PAST %>% 
   group_by(key) %>% 
   dplyr::summarise(mean=mean(value, na.rm = T), sd=sd(value,na.rm=T), 
             n=n(),
             se=sd/sqrt(n),
             tscore=qt(1-0.05/2, n-1),
             zscore=1.645, #alpha=0.05
             tme=tscore*se,
             zme=zscore*se,
             tlower.ci=mean-tme,
             tupper.ci=mean+tme,
             zlower.ci=mean-zme,
             zupper.ci=mean+zme,
             max=max(value, na.rm=T),min=min(value, na.rm = T)
   )
library(DT)
table1 <- datatable(long_df, extensions = "Buttons",caption = "CI 95%",
          filter = "top",
          options = list(dom="Blfrtip",buttons=c("copy","csv","excel","pdf","print"), lengthMenu=list(c(10,25,50,-1), c(10,25,50,"All")),pageLength=25))

table1

```

### NA  Missing data

```{r echo=FALSE}
library(ggplot2)
PAST_num1 <- PAST_num %>% as.data.frame();colSums(is.na(PAST_num1))
fig3 <- ggplot(PAST_num1, aes( x=ases_index_0_100 , y=sane_score_0_100 , color=bmi_body_mass_index )) +
  geom_point(show.legend = T) +
  labs( x="ASES", y="SANE", title = "ASE vs. SANE", color="bmi_body_mass_index") +
  scale_color_gradient(low="green", high ="red", na.value ="blue", guide = "legend") +
  theme_minimal() + theme(legend.position = "bottom")
 fig3
```
```{r eval=FALSE, include=FALSE}
library(mice)
library(VIM)
set.seed(2222)
imputeIBM <- mice(PAST_num1,m=3,seed=123)
imputeIBM$imp$bmi_body_mass_index
imputeIBM$imp$symptom_duration_months

imp_PASTA <- complete(imputeIBM,1)
imp_PASTA$total_score <- imp_PASTA$sane_score_0_100+imp_PASTA$ases_index_0_100
#head(imp_PASTA)
### imputation for categories
PAST_ch <- PASTA_Data1 %>% 
  dplyr::select(is.character) %>% 
  dplyr::select(-22,-23,-25,-26) %>% 
  mutate(as.factor)
set.seed(333)
imputeall <- mice(PASTA_Data1 ,remove.collinear=FALSE)
imputeall$imp$dominant_side
colSums(is.na(PAST_ch))
colnames(PAST_ch)

```


### mean and CI for numeric valus for completed BMI data

```{r}

mean_all <- sapply(imp_PASTA, Rmisc::CI )
mean_CI <- as.data.frame(t(mean_all))
mean_CI$variables <- rownames(mean_CI)
  
colnames(mean_CI) <-  c("upper.ci","mean","lower.ci","variables")
head(mean_CI,20)
sd(imp_PASTA$bmi_body_mass_index)

```

### Does age:end affect outcome scores or inability to meet MCID, SCB, PASS for the SANE or ASES index scores (column AC – AM), please calculate relationship against each individually.	

```{r eval=FALSE, include=FALSE}

 
ch_past <- PASTA_Data1 %>% 
  select(!is.numeric)
imp_past_data <- cbind(ch_past,imp_PASTA)

imp_past_data1 <- imp_past_data %>% 
   mutate(tobacco_use=factor(tobacco_use)) %>% 
   mutate(tobacco_use = ifelse((tobacco_use == "F" | tobacco_use== "Y"), "Y","N"))
 colnames(imp_past_data1)
table(tobacco=imp_past_data1$tobacco_use, pass=imp_past_data1$pass_total_ases_sane_n_no_y_yes)
```


### total scores CI by pass

```{r echo=FALSE, message=FALSE, warning=FALSE}
#write.csv(imp_past_data1, "imp_past_data1.csv")
library(readr)
imp_past_data1 <- read_csv("G:/My Drive/#1_Jay's Space/Andrews_Insititute/PASTA/imp_past_data1.csv", 
    col_types = cols(X1 = col_skip()))

past_pass <- imp_past_data1 %>% 
  dplyr::group_by(pass_total_ases_sane_n_no_y_yes) %>% 
  dplyr::summarise(
    count=n(),
    percN=count/106*100,
    mean = mean(total_score),
    lci = t.test(total_score, conf.level = 0.95)$conf.int[1],
    uci = t.test(total_score, conf.level = 0.95)$conf.int[2],
    min=min(total_score),
    max=max(total_score)
  )

past_pass

```


### Normality test 

```{r}
shapiro.test(imp_past_data1$ases_index_0_100)
#hist(imp_past_data1$ases_index_0_100)
#tran1 <- sqrt(imp_past_data1$ases_index_0_100)
hist(tran1)

```



### code data set

```{r include=FALSE}
filter_data1 <- imp_past_data1 %>% 
   filter(rheumatoid_arthritis_yes_no=="N") %>% 
  filter(previous_surgery=="N") %>% 
  filter(subacromial_decrompression=="Y") %>% 
  filter(further_surgery_performed=="N") %>% 
  dplyr::select(-rheumatoid_arthritis_yes_no,-previous_surgery,-subacromial_decrompression, -further_surgery_performed)
  
data_past_model <- imp_past_data1 %>% 
  filter(rheumatoid_arthritis_yes_no=="N") %>% 
  filter(previous_surgery=="N") %>% 
  filter(subacromial_decrompression=="Y") %>% 
  filter(further_surgery_performed=="N") %>% 
  filter(cr_capsular_release_surgery == "N") %>% 
  dplyr::select(pass_total_ases_sane_n_no_y_yes,sex,
         workers_compe_ation_claim, traumatic_history,
         diabetes, tobacco_use,
          gout_yes_no,
         anxiety_depression_yes_no,physical_therapy_yes_no,
         laborer_yes_no, athlete,
         steroid_injection, 
         side_of_surgery_right_left, 
         dce_distal_clavicle_excision_surgery, labral_repair_surgery,
         bt_biceps_tenodesis_surgery, 
         29:40) %>% 
         na.omit() %>% #104
     mutate(shoulder_arthritis_grade_0_4=as.factor(shoulder_arthritis_grade_0_4)) %>% 
     mutate(pass_total=as.factor(pass_total_ases_sane_n_no_y_yes)) %>% 
  mutate(BMI = ifelse(bmi_body_mass_index<=18.5,"underweight",
                      ifelse(bmi_body_mass_index<= 24.9, "normal",
                             ifelse(bmi_body_mass_index<= 29.9 ,"overweight","obesity")))) %>% 
  dplyr::select(-1)

 
```



```{r}
#recede for reference
#write.csv(data_past_model, "data_past_model.csv")
colnames(data_past_model)
```
### liner regression by ASES and SAES scores

```{r}
#linear regression with all vari
 
summary(regression_1 <- lm(sqrt(sane_score_0_100) ~ ., data= data_past_model[,c(2:22,23,29)]))
summary(regression_2 <- lm(sqrt(ases_index_0_100) ~ ., data= data_past_model[,c(2:22,26,29)]))

```
```{r eval=FALSE, include=FALSE}
addmargins(table(data_past_model$gout_yes_no, data_past_model$pass_total))
chisq.test(table(data_past_model$BMI, data_past_model$pass_total))
```
 
```{r eval=FALSE, include=FALSE}
library(pander)
odd_past_data <- data_past_mode3 %>% 
  mutate(gout_yes_no1=ifelse(gout_yes_no=="Y", 1,0)) %>% 
  group_by(gout_yes_no1, pass_total) %>% 
  dplyr::summarise(freq =n()) %>% 
  mutate(all=sum(freq), prob=freq/all, odds=prob/(1-prob), logodds=log(odds)) %>% 
  round(., 5)
pander(odd_past_data)
```

## recode variables

```{r message=FALSE, warning=FALSE, include=FALSE}
colnames(data_past_model)
library(dplyr)
data_past_mode2 <- data_past_model %>% 
   dplyr::select(pass_total,sex,
         workers_compe_ation_claim, traumatic_history,
         diabetes, tobacco_use,
          gout_yes_no,
         anxiety_depression_yes_no,physical_therapy_yes_no,
         laborer_yes_no, athlete,
         steroid_injection, 
         side_of_surgery_right_left, 
         dce_distal_clavicle_excision_surgery, labral_repair_surgery,
         bt_biceps_tenodesis_surgery, 
         16:21) %>% 
   mutate(BMI2 = ifelse(bmi_body_mass_index<=24.9,"under24.9","over24.9")) %>% 
  mutate(sizerotator2=ifelse(size_rotator_cuff_tear_size_percent<70,"size<70", "size>=70")) %>% 
                            #  ifelse(size_rotator_cuff_tear_size_percent<75,"60<=size<75","size>=75"))) %>% 
  mutate(SDM2=ifelse(symptom_duration_months<=3,"SDM<=3months",
                     ifelse(symptom_duration_months<=6,"SDM<=6months","SDM>6months"))) %>% 
  mutate(AGE2=ifelse(age<40,"AGE<40",
                     ifelse(age<50,"40<=AGE<50",
                            ifelse(age<60,"50<=AEG<60","AGE>=60")))) %>% 
  mutate(FUY=ifelse(follow_up_years<=2,"FUY<=2yrs","FUY>2yrs")) %>% 
  mutate(shoulder_arthritis_yes_no = ifelse(  (shoulder_arthritis_grade_0_4 == c("0")), "grade0", 
                                              ifelse(shoulder_arthritis_grade_0_4 ==c("1","2"), "grade1to2","grade3to4"))) %>% 
  dplyr::select(-bmi_body_mass_index,-size_rotator_cuff_tear_size_percent,-symptom_duration_months,-age,-follow_up_years,-shoulder_arthritis_grade_0_4) 

### reference code
data_past_mode3 <-   data_past_mode2 %>% 
 dplyr::mutate(across(where(is.character),  as.factor)) %>% 
     mutate(gout_yes_no = relevel(gout_yes_no, ref="Y")) %>% #74
   mutate(sex = relevel(sex, ref="F"),
          diabetes = relevel(diabetes, ref="Y"),
          tobacco_use = relevel(tobacco_use, ref="Y"),
          traumatic_history = relevel(traumatic_history, ref="Y"),
          workers_compe_ation_claim = relevel(workers_compe_ation_claim, ref="Y"),
          anxiety_depression_yes_no = relevel(anxiety_depression_yes_no, ref="Y"),
          physical_therapy_yes_no= relevel(physical_therapy_yes_no, ref="N"),
          laborer_yes_no = relevel(laborer_yes_no, ref="N"),
          athlete = relevel(athlete, ref="Y"),
          steroid_injection=relevel(steroid_injection, ref="N"),
          side_of_surgery_right_left= relevel(side_of_surgery_right_left, ref="L"),
          dce_distal_clavicle_excision_surgery=relevel(dce_distal_clavicle_excision_surgery, ref="Y"),
          labral_repair_surgery = relevel(labral_repair_surgery, ref="Y"),
          bt_biceps_tenodesis_surgery = relevel(bt_biceps_tenodesis_surgery, ref="Y"),
          #C = relevel(cr_capsular_release_surgery, ref="Y"),
          shoulder_arthritis_yes_no = relevel(shoulder_arthritis_yes_no, ref="grade0"),
          BMI2 = relevel(BMI2, ref="under24.9"),
          sizerotator2 = relevel(sizerotator2, ref="size<70"),
          SDM2= relevel(SDM2, ref="SDM>6months"),
          AGE2 = relevel(AGE2, ref="AGE>=60"),
          FUY = relevel(FUY, ref="FUY>2yrs")
          )   

set.seed(12344)
summary(modela <- glm(pass_total ~ ., family = "binomial", data = data_past_mode3))


exp(cbind(OR= coef(modela), confint(modela)))
library(sjPlot)
tab_test <- tab_model(modela, CSS = css_theme("cells"))
tab_test
library(flextable)
gt_r1 <- glm(pass_total~., data_past_mode3, family = binomial) %>%
  tbl_regression(exponentiate = TRUE) 
muytable1 <- gt_r1 %>% as_flex_table()

colnames(data_past_mode3)
stats::chisq.test(table(data_past_mode3$sizerotator2, data_past_mode3$pass_total))
```
 
```{r eval=FALSE, include=FALSE}
#colnames(filter_data1)
summary(regression_a <- glm( factor(pass_n_no_y_yes) ~ ., family = "binomial", data= filter_data1[,c(2:18,26:31,21)]))
summary(regression_b <- glm( factor(pass_n_no_y_yes_3) ~ ., family = "binomial",data= filter_data1[,c(2:18,26:31,24)]))


```


### logistic regression - releveling factors(reparameterizing model)

```{r echo=FALSE, message=FALSE, warning=FALSE}


set.seed(222)
summary(modelb <- glm(pass_total ~ gout_yes_no*shoulder_arthritis_grade_0_4, family = "binomial", data = data_past_mode3))
set.seed(333)
summary(modelc <- glm(pass_total ~ sex*athlete*AGE2*traumatic_history, family = "binomial", data = data_past_mode3))
set.seed(444)
summary(modeld <- glm(pass_total ~ AGE2+ labral_repair_surgery+gout_yes_no + BMI2 + shoulder_arthritis_grade_0_4, family = "binomial", data = data_past_mode3))
set.seed(555)
summary(modele <- glm(pass_total ~ SDM2+AGE2+ BMI2 + shoulder_arthritis_grade_0_4+gout_yes_no+labral_repair_surgery, family = "binomial", data = data_past_mode3))

model_ser <- c("modela","modelb","modelc","modeld","modele")
AIC <- c(100.86,103.11,102.33,92.82,90.423)
## estimate for intercept: the log odds of a all factors are zero values
#coefficient for numerical factor==1.511e+00 which is interpreted as the expected change in log odds for a one-unit increase in numerical factor
#estimate means +estimationg increase mean outcome values
# chategory A and B: expect mean outcome to be estimate +- than reference level
#table(pass=data_past_mode3$pass_total, gout=data_past_mode3$gout_yes_no)
```
### CI and OR
```{r}
exp(cbind(OR= coef(modela), confint(modela)))
library(sjPlot)
tab_test <- tab_model(modela, CSS = css_theme("cells"))
tab_test


```





###anova model
```{r}
anova(modela, modeld, test = "Chisq")

```

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
 
set.seed(12344)
summary(modela <- glm(total_pass ~ ., family = "binomial", data = model_data[,c(1:19,31)]))
 modela <- glm(total_pass ~ ., family = "binomial", data = model_data[,c(1:21,33)])


exp(cbind(OR= coef(modela), confint(modela)))
library(sjPlot)
tab_test <- tab_model(modela, CSS = css_theme("cells"))





library(logistf)
logistf_r1 <- logistf(data = model_data[,c(1:21,33)], total_pass~.,  firth = TRUE, pl=TRUE)
logistf_r2 <- logistf(data = model_data[,c(1:21,33)], total_pass~.,  firth = TRUE, pl=TRUE) %>%
  tbl_regression(exponentiate = TRUE)  %>% 
  modify_header(list(label ~ "**Variables**")) %>% 
  as_flex_table()

logistf_r2
muytable1

summary(logistf_r1)
logistf_r1$table_body
exp(coef(logistf_r1))
logistf_r1$conv
```
 


```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

gt_asesF <- lm(ases_func_score~., model_data[1:22]) %>%
  tbl_regression() 

gt_vas <- lm(vas_score~., model_data[,c(1:21,23)]) %>%
  tbl_regression( )

gt_asesindex <- lm(ases_index~., model_data[,c(1:21,24)] ) %>%
  tbl_regression()
  
gt_asespass <-  glm(ases_pass~., model_data[,c(1:21,27)], family = binomial) %>%
  tbl_regression(exponentiate = TRUE)

gt_t1 <- model_data %>% 
  tbl_summary(missing = "no") %>% 
  add_n() %>%
  modify_header(stat_0 ~ "**n (%)**") %>%
  modify_footnote(stat_0 ~ NA_character_)

theme_gtsummary_compact()
#> Setting theme `Compact`
ases_all_table <- tbl_merge(
  list(gt_t1,gt_asesF, gt_vas ),
  tab_spanner = c(NA_character_, "**ASES Function Score(lm)**","**VAS Score(lm)**")
) %>%  as_flex_table()



ases_all_table34 <-   tbl_merge(
  list(gt_t1, gt_asesindex, gt_asespass),
  tab_spanner = c(NA_character_,"**ASES Index(lm)**",
                  "**ASES Pass(glm)**")
) %>%  as_flex_table()


ases_all_table
ases_all_table34

```


### estimate

```{r}
output1 <- tidy(modela)
r1 <- datatable(output1, extensions = "Buttons",caption = "Results Table 1",
          filter = "top",
          options = list(dom="Blfrtip",buttons=c("copy","csv","excel","pdf","print"), lengthMenu=list(c(10,25,50,-1), c(10,25,50,"All")),pageLength=25))
r1



```

### coefficient and CI

```{r}
library(MASS)
mycoef <- as.data.frame(coef(modela)) %>% 
  mutate(exp_coef=exp(coef(modela))) 

# for every one age increase in surgery, the odds of the passing increase by a factor of 1.001461+00
# exp(coef)=values means we expect to see about (1-exp(value))% increase in the odds of being passing 
### confidence intervals

 

conf1 <- confint(modela)
r2 <- datatable(conf1, extensions = "Buttons",caption = "CI Table 1",
          filter = "top",
          options = list(dom="Blfrtip",buttons=c("copy","csv","excel","pdf","print"), lengthMenu=list(c(10,25,50,-1), c(10,25,50,"All")),pageLength=25))
r2

```


###predicted

```{r}
data_past_mode3$pred <- predict(modela,type="resp")
as.data.frame(data_past_mode3[1:10,])
```





### vari imp
```{r}

imp_vari <- (caret::varImp(modela)) 
imp_vari 


```

### prediction
```{r}

data_past_mode3$code_pred <-  ifelse(data_past_mode3$pred > 0.5, 1,0)
tab1 <- table(Predicted = data_past_mode3$code_pred, Actual = data_past_mode3$pass_total)
tab1
### error
1-sum(diag(tab1))/sum(tab1)
```
### goodness of fit test and plot ROCR

```{r}
hist(modela$fitted.values)
fitvalue <- modela$fitted.values
with(modela, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = F))

library(ROCR)

rocr_pred <- prediction(data_past_mode3$pred, data_past_mode3$pass_total)
rocr_perf <- performance(rocr_pred, "tpr", "fpr")

plot(rocr_perf, colorize= TRUE, print.cutoffs.at=seq(0.1, by=0.1))

```
### prediction #2

```{r}
data_past_mode3$code_pred2 <-  ifelse(data_past_mode3$pred > 0.60, 1,0)
tab2 <- table(Predicted = data_past_mode3$code_pred2, Actual = data_past_mode3$pass_total)
tab2
### error
1-sum(diag(tab2))/sum(tab2)
```






### plot for gender

```{r}
data_past_model %>% 
  mutate(prob = ifelse(pass_total == "Y", 1, 0)) %>% 
  ggplot(aes(x=sex, prob)) +
  geom_point(alpha = 0.15) +
  geom_smooth(method = "glm", method.args = list(family = "binomial")) +
  ggtitle("Logistic regression Fit") +
  xlab("gender") +
  ylab("Probability of Pass")
```

### plot for residuals (+-3sd)

```{r}
library(modelr)
model1_data <- augment(modela) %>% 
  dplyr::mutate(index = 1:n())

ggplot(model1_data, aes(index, .std.resid, color = pass_total)) + 
  geom_point(alpha = .9) +
  geom_ref_line(h = 3)





```

